%-------------------------
% Resume in Latex
% Author : Deepak Yadav
% Website: https://github.com/deepak7376/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Deepak Yadav} & Email: \href{mailto:dky.united@gmail.com}{dky.united@gmail.com}\\
  Consultant at Sony (AI and Machine Learning) & Mobile: +91-9836375132 \\
  \href{https://www.linkedin.com/in/dky7376}{www.linkedin.com/in/dky7376} & \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Engineering Science And Technology}{Howrah, WB}
      {Master of Technology in Information Technology;  GPA: (7.0/10.0)}{Aug. 2017 -- June. 2019}
    \resumeItemListStart
        \resumeItem{Relevant Coursework}
          {Machine Learning, Algorithms, Information and Coding Theory, Advanced Database Management System.}
      \resumeItemListEnd
    \resumeSubheading
      {United College of Engineering and Research}{Allahabad, UP}
      {Bachelor of Technology in Electronics and Communication Engineering;  GPA:(6.8/10.0)}{Aug. 2010 -- July. 2014}
    \resumeItemListStart
        \resumeItem{Relevant Coursework}
          {Signal and Systems, Microprocessors, VLSI Design and Embedded System.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience (4.5 years)}
\resumeSubHeadingListStart

  \resumeSubheading
    {Sony}{Bengaluru, Karnataka}
    {Consultant}{Jun 2021 - Present}
    \resumeItemListStart
      \resumeItem{Objective}
        {Constructing a versatile framework to facilitate the effortless evaluation of the accuracy of diverse deep learning models on the IMX500 Intelligent Vision Sensor device.}
      \resumeItem{Contribution}
        {Developed a comprehensive framework capable of seamlessly accommodating various state-of-the-art machine learning models, including classification, object detection, and semantic segmentation. Assessed the accuracy of these models on IMX500 devices, ensuring reliable performance across different use cases.}
      \resumeItem{Tools}
        {Tensorflow, Pytorch, Scikit-learn, Python, Streamlit, Object-oriented design.}
    \resumeItemListEnd

  \resumeSubheading
    {Activa Inc.}{Hyderabad, Telangana}
    {Associate Data Scientist}{Dec 2019 - Apr 2021}
    \resumeItemListStart
      \resumeItem{Objective}
        {Building an automated AI platform that works with tabular data, raw text, time series, and images.}
      \resumeItem{Contribution}
        {Automated the time series forecasting pipeline using a genetic algorithm, resulting in a significant reduction in training time. Implemented distributed training across multiple GPUs for performance optimization. Deployed models automatically across a variety of environments, including creating a REST endpoint and running as a service in the cloud.}
      \resumeItem{Tools}
        {Tensorflow, Pytorch, Scikit-learn, Python, Docker, Flask, AWS EC2, AWS Kinesis, REST, CI/CD.}
    \resumeItemListEnd

  \resumeSubheading
    {Activa Inc.}{Hyderabad, Telangana}
    {Data Science Intern}{Aug 2019 - Dec 2019}
    \resumeItemListStart
      \resumeItem{Objective}
        {Developed a proof of concept (PoC) for United Technologies Corp. (UTC) to automate aircraft engine internal crack detection.}
      \resumeItem{Contribution}
        {Built a computer vision model using Mask-RCNN that can easily detect cracks in the internal parts of the engine.}
      \resumeItem{Tools}
        {Computer Vision, Object Detection, Instance Segmentation, Mask-RCNN, Python, Tensorflow, OpenCV.}
    \resumeItemListEnd

  \resumeSubheading
    {IIEST Shibpur}{Howrah, WB}
    {Postgraduate Researcher}{July 2018 - June 2019}
    \resumeItemListStart
      \resumeItem{Objective}
        {Fault Detection in Wireless Sensor Networks (WSNs).}
      \resumeItem{Contribution}
        {Conducted a comprehensive comparative analysis of statistical and machine learning methods for fault detection in Wireless Sensor Networks (WSNs). Developed a robust algorithm that effectively identifies faulty nodes in WSNs, resulting in enhanced accuracy compared to existing methods. The designed algorithm significantly improves the detection capabilities, providing a reliable solution for fault identification in WSNs.}
     \resumeItem{Tools}
      {Python, Machine Learning, Statistics, IoT, Sensor Networks.}
    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Open Source Projects}
\resumeSubHeadingListStart
  \resumeSubItem{\href{https://github.com/deepak7376/robustbase}{Robustbase}}
    {Open Source Python library for statistical estimation with 23,000+ downloads.}
  \resumeSubItem{\href{https://github.com/deepak7376/HyperTune}{HyperTune}}
    {Open source hyper-parameter optimization library using genetic algorithms.}
  \resumeSubItem{\href{https://github.com/deepak7376/WSNFault}{WSNFault}}
    {Statistical fault detection algorithm for Wireless Sensor Networks (WSNs).}
  \resumeSubItem{\href{https://github.com/deepak7376/downcast}{downcast}}
    {Automatic reduction of pandas data frame size with 44,000+ downloads.}
  \resumeSubItem{\href{https://github.com/deepak7376/complex}{complex}}
    {Compute complex number operations: addition, subtraction, multiplication, division, and modulus with 32,000+ downloads.}
\resumeSubHeadingListEnd



% %--------PROGRAMMING SKILLS------------
% \section{Programming Skills}
% \resumeSubHeadingListStart
%   \item \textbf{Languages}: Python, C++, SQL
%   \item \textbf{Machine Learning}: Computer Vision, Natural Language Processing, ETL, Data science pipeline (cleansing, wrangling, visualization, modeling, interpretation), Statistics, Time series, etc.
%   \item \textbf{Software Engineering}: Object-Oriented Programming, Data Structure and Algorithms
%   \item \textbf{Back-end}: Flask, REST API, AWS EC2, AWS Kinesis, AWS Firehose, AWS IoT Core, AWS Lambda, AWS DynamoDB, AWS S3, CI/CD pipeline, Git.
% \resumeSubHeadingListEnd


%--------Extracurricular Activities------------
% \section{Extracurricular Activities}
% \resumeSubHeadingListStart
%   \item{
%     \textbf{Cricket}:
%     \begin{itemize}
%       \item Played competitive cricket at the district level for three years.
%       \item Participated in multiple inter-school and inter-college cricket tournaments.
%       \item Developed strong teamwork and leadership skills through regular practice sessions and matches.
%     \end{itemize}
%   }
%   \item{
%     \textbf{Swimming}:
%     \begin{itemize}
%       \item Trained in swimming for five years, achieving an intermediate level of proficiency.
%       \item Participated in various swimming competitions, including local and regional events.
%       \item Developed excellent endurance, discipline, and focus through regular training sessions.
%     \end{itemize}
%   }
% \resumeSubHeadingListEnd

\end{document}
